### 2018-10-12 Manuscript/Manuscript.tex

To determine whether there is a relationship between Earth's climate state and tropical LIP area, we compared these areas to a compilation of the latitudinal extent of continental ice sheets through time \fig{}

@@

@@

LIP Location map
Panel A) 0 to 500 Ma
Panel B) 500 to 1200 Ma

LIP fractional area remaining with time

@@

LIP area through the tropics through time
Panel A) ice extent
Panel B) all latitude 
Panel C) in the tropics (different models)
Panel D) heat map of one of the models

Monte Carlo null hypothesis test
Panel A) total LIP
Panel B) LIP in the tropics
Panel C) continental fraction in the tropics
Panel D) sutures(??)

\footnotesize

>>>>

To determine whether there is a relationship between Earth's climate state and tropical LIP area, we compared these areas to a compilation of the latitudinal extent of continental ice sheets through time \fig{}. WHY NOT USING CO2?

@@

DISCUSS FRANKLIN AND UMKONDO AREAS AND COMPARE TO THE PHANEROZOIC RECORD.

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{Map of current extent of lithologies associated with LIPs and estimates of the initial LIP area.}}
	\label{fig:LIP_map}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{LIP area through the tropics through time
Panel A) ice extent
Panel B) all latitude 
Panel C) in the tropics (different models)
Panel D) heat map of one of the models}}
	\label{fig:LIP_area}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{Monte Carlo null hypothesis test
Panel A) total LIP
Panel B) LIP in the tropics
Panel C) continental fraction in the tropics
Panel D) sutures(?)}}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

\newpage
\footnotesize
